On Secure Delegation of SampBQP with a Classical Client

### 2019-11-25 preliminaries.tex
Add delta parameter to soundness

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

>>>>

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

### 2019-11-25 qpip.tex
Add delta parameter to soundness

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $\BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

@@

TODO the following needs $\delta$ parameter
\begin{theorem}
	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $1-O(T^{-c})$ for any constant $c$.
\end{theorem}
\begin{proof}

	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so by Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $q'=P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

@@

	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover. Let $\sigma$ be the state the prover sends.

>>>>

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $(\delta, s)$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $\BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $(O(T^{-c}), 1-O(T^{-c}))$ for any constant $c$.
\end{theorem}
\begin{proof}
	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so by Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $q'=P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

@@

	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends.
